---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mentordash

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of mentordash is to create a dashboard for mentors at the [R4DS Online Learning Community](https://www.rfordatasci.com/).

## Installation

You can install the released version of mentordash from [CRAN](https://CRAN.R-project.org) with:

``` r
# Nope.
# install.packages("mentordash")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("r4ds/mentordash")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mentordash)
## basic example code coming soon.
```

## Code of Conduct

Please note that the 'mentordash' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
